### 2025-01-15 manuscript.tex
Started to explain TWS API and collected data.

\chapter{Gyakorlati rész}
\section{MATLAB\textsuperscript{\textcopyright}}
MATLAB is a numeric computing environment that provides a wide range of tools and utilities, including a programming language, an integrated development environment (IDE) for code editing, interactive apps, and specialized libraries for solving domain-specific problems such as image processing, control system design, and data analysis. With its built-in functions and pre-made algorithms, MATLAB is widely used by engineers and researchers to design, develop, and operate complex systems across various industries. Applications include, but are not limited to, but not limited to autonomous vehicles, aircraft, marine vehicles, spacecraft, semiconductor design, wireless communication systems and manufacturing optimization. \cite{WhatIsMATLAB}\\
MATLAB offers another product called Simulink, which provides tools for Model-Based Systems Engineering (MBSE). Simulink enables developers to design, simulate, and deploy systems following a model-based architecture. It is primarily used to virtually simulate systems before physical testing or hardware deployment, evaluate system designs and compose control architectures. \cite{WhatIsSimulink} Simulink is also utilized for creating machine learning systems through reinforcement learning. Using this package, intelligent agents can be trained via the standard trial-and-error interactions with dynamic environments. \cite{SimulinkAI}\\
MATLAB is not a free product but offers various license types with different pricing, including a free license for students at partner institutions. \cite{MATLABPricing} Due to its extensive tools and libraries, as well as the availability of the free student license, we chose MATLAB as the platform for developing the program for this thesis.\\

\section{IBKR API}

>>>>

\chapter{Gyakorlati rész}
\section{MATLAB\textsuperscript{\textcopyright}}
MATLAB is a numeric computing environment that provides a wide range of tools and utilities, including a programming language, an integrated development environment (IDE) for code editing, interactive apps, and specialized libraries for solving domain-specific problems such as image processing, control system design, and data analysis. With its built-in functions and pre-made algorithms, MATLAB is widely used by engineers and researchers to design, develop, and operate complex systems across various industries. Applications include, but are not limited to, but not limited to autonomous vehicles, aircraft, marine vehicles, spacecraft, semiconductor design, wireless communication systems and manufacturing optimization. \cite{WhatIsMATLAB}\\
MATLAB offers another product called Simulink, which provides tools for Model-Based Systems Engineering (MBSE). Simulink enables developers to design, simulate, and deploy systems following a model-based architecture. It is primarily used to virtually simulate systems before physical testing or hardware deployment, evaluate system designs and compose control architectures. \cite{WhatIsSimulink} Simulink is also utilized for creating machine learning systems through reinforcement learning. Using this package, intelligent agents can be trained via the standard trial-and-error interactions with dynamic environments. \cite{SimulinkAI}\\
MATLAB is not a free product but offers various license types with different pricing, including a free license for students at partner institutions. \cite{MATLABPricing} Due to its extensive tools and libraries, as well as the availability of the free student license, we chose MATLAB as the framework for developing the program for this thesis.\\

\section{The data}
The Trader Workstation (TWS) is an online platform created by Interactive Brokers (IBKR) that traders and investors use to trade stocks, bonds, futures, and more across over 150 markets worldwide via its graphical user interface. \cite{TW} TWS also offers a non-graphical API designed for fast-paced, data-sensitive, and complex programmatic trading. This API can handle thousands of market data streams simultaneously while allowing users to execute trades. \cite{IBKRAPI}.\\ 
Using this API, various types of data can be collected, including Top Market Data (Level 1) and Market Depth data (Level 2). Level 1 data includes the best bid and ask prices, along with the number of shares that traders are trying to buy or sell. It essentially represents the top of the limit order book for both sides. \cite{IL1} Level 2 data expands the information provided by Level 1 by adding the market depth, typically showing about 5-10 additional price levels. This type of data includes not only the best bid and ask prices but also some of the subsequent lines in the limit order book. \cite{IL2}\\
HOW LIMIT ORDER BOOKS ARE LOADED\\
EXPLAIN THE STRUCTURE AND MEANING OF OUR DATA\\
PIC OF DATA?\\

\section{LOB reconstruction}
